Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-11-09 prop_letter.tex
prop_letter.tex \section{The Kochen-Specker Theorem and Contextuality} Updating...

>>>>

For two-dimensional Hilbert space, there exists a non-contextual hidden
variable model~\cite{kochenspecker1967,BellBook1987}. This non-contextual
model can be represented as a quantum probability measure $\mu:\events\rightarrow[0,1]$
satisfying an extra condition, either $\mu\left(P\right)=0$ or~$1$,
but not any intermediate values. A quantum probability measure of
this kind, $\mu$, is equivalent to a 0-deterministic QIVPM $\bar{\mu}:\events\rightarrow\left\{ \imposs,\necess\right\} $
since the latter can be constructed according to the following way:
\begin{equation}
\bar{\mu}\left(P\right)=\begin{cases}
\imposs\,, & \textrm{ if }\mu\left(P\right)=0\:;\\
\necess\,, & \textrm{ if }\mu\left(P\right)=1\:,
\end{cases}
\end{equation}
and vice versa. Moreover, the QIVPM~$\bar{\mu}$ is also $\delta$-deterministic
for any $\delta\in\left[0,1\right]$ since $\imposs\subseteq\left[0,\delta\right]$
and $\necess\subseteq\left[1-\delta,1\right]$. Conversely, as shown
in the proof of Thm.~\ref{cor:Kochen-Specker-IVPM}, any $\delta$-deterministic
QIVPM for $\delta<\frac{1}{3}$ induces a 0-deterministic QIVPM so
as a non-contextual hidden variable model. In summary, the existence
of $\delta$-deterministic QIVPM for $\delta<\frac{1}{3}$ is equivalent
to the existence of a non-contextual hidden variable model. Both of
them exist for $d=2$, while none of them exist for $d\ge3$.
